---
title: "Cumulative"
format: html
author: Anish Talla
execute: 
  echo: false
---

```{r}
#| label: setup
#| message: false

library(tidyverse)
library(primer.data)
library(tidymodels)
library(gtsummary)
library(equatiomatic)
library(marginaleffects)
```


```{r}
# Prepare data
x <- ces |> 
  filter(year == 2020) |>
  select(approval, education, faminc, ideology) |>
  drop_na() |>
  slice_sample(n = 2000)
```


```{r}
#| label: model
#| cache: true

fit_approval <- MASS::polr(approval ~ ideology + faminc + education, data = x)
```


```{r}
#| label: plot

temp <- plot_predictions(fit_approval, 
                        condition = c("ideology"),
                        draw = FALSE)

ggplot(temp, aes(x = ideology, y = estimate, fill = group)) +
  geom_bar(stat = "identity") +
  scale_fill_brewer(palette = "RdBu") +
  geom_text(aes(label = sprintf("%.2f", estimate)),
            position = position_stack(vjust = 0.5), size = 3) +
  coord_flip() +
  labs(title = "Predicted Approval by Ideology",
       x = "Ideology",
       y = "Estimated Probability",
       fill = "Approval Level") +
  theme_minimal() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))

```

With CES data, we’re studying how presidential approval relates to ideology in 2020, but we have to consider that survey participants might not fully represent all Americans. Our cumulative ordinal regression model suggests that people who are very conservative are about 5.6 units higher in presidential approval than those who are very liberal, with a 95% confidence interval from 4.9 to 6.2.


```{r}
#| label: math

extract_eq(fit_approval, 
           intercept = "beta", 
           use_coefs = TRUE)
```


```{r}
#| label: table

tbl_regression(fit_approval)
```